Articles Of Association

### 2014-12-08 Articles_of_Association_Melbourne_Bitcoin_Technology_Centre_MBTC_2015.tex
Update formatting of article enumartion
Automate current date
Added clarification of Association Entity from MBTC Space

% Language package
\usepackage[english]{babel}
% Input character encoding
\usepackage[utf8]{inputenc}
% Font encoding package
\usepackage{fontenc}
% Document layout package
\usepackage[top=2.25cm, bottom=3cm, left=2.5cm, right=2.5cm]{geometry}
% PDF document link package
\usepackage{hyperref}

@@

  \author{BITCOIN TECHNOLOGY CENTERS, INC.} 
  \title{Articles Of Association} 
  \date{Mon 17 Nov, 2014} 
  \maketitle

@@

  \section*{\centerline{BITCOIN TECHNOLOGY CENTERS, INC.}}

@@

    \item Interpretation

@@

    \item Identity

@@

      \item The incorporated association, is to be known as "Bitcoin Technology Centres, Inc." in all holdings.

@@

>>>>

% Language package
\usepackage[english]{babel}
% Input character encoding
\usepackage[utf8]{inputenc}
% Font encoding package
\usepackage{fontenc}
% Document layout package
\usepackage[top=2.25cm, bottom=3cm, left=2.5cm, right=2.5cm]{geometry}
% PDF document link package
\usepackage{hyperref}
% Allow for enumeration prefix
\usepackage{enumitem}
% Add date formatting function
\usepackage{datetime}

@@

  \author{MELBOURNE BITCOIN TECHNOLOGY CENTER, INC.} 
  \title{Articles Of Association} 
  \shortdate
  \maketitle

@@

  \section*{\centerline{MELBOURNE BITCOIN TECHNOLOGY CENTER, INC.}}

@@

    \\Definitions \& Interpretation 

@@

    \begin{enumerate}[label=Article \arabic*.,itemindent=*]
    \item Name

@@

      \item An incorporated association has been established under the name ``Melbourne Bitcoin Technology Center, Inc." in all holdings.
    \item Head Office
      \item The Association is domiciled in Victoria.

@@

    \item Activity
      \item ``Melbourne Bitcoin Technology Center, Inc." presently assists in the operation of the ``Melbourne Bitcoin Technology Center".
      \item ``Melbourne Bitcoin Technology Center" may be also be referred to as ``MBTC"  in publications, communication and common use.
      \item ``MBTC" does not, and shall not be deemed to refer to the association Melbourne Bitcoin Technology Center, Inc.
